\cvsection{Relevant Projects}

\begin{cventries}
  \cventry
    {\href{https://github.com/sam-taiff/pet-food-loyalty-tracker}{\faLink \space https://github.com/sam-taiff/pet-food-loyalty-tracker}}
    {Loyalty Tracking System}
    {Christchurch, New Zealand} % Empty location
    {} % Empty date
    {
      \begin{cvitems}
        \item {Developed a full-stack web application to track pet food purchases and rewards in conjunction with Pet Central as a stakeholder.}
        \item {Utilised \textbf{PostgreSQL} and \textbf{Supabase} to store customer data and rewards.}
        \item {Implemented a \textbf{RESTful API} using \textbf{Node.js} and \textbf{Express} to interact with the database.}
        \item {Created a user-friendly interface with \textbf{React.js} for customers to manage their rewards.}
        \item {The application is currently in production use and serves as a proof of concept for future development.}
      \end{cvitems}
    }

  \cventry
    {} % Empty position
    {Supercapacitor-assisted whiteware} % Project
    {University of Auckland} % Empty location
    {} % Empty date
    {
      \begin{cvitems}
        \item {Eliminated the need for Maximum Power Point Tracking to improve efficiency of soloar production by up to \textbf{15\%.}}
        \item {Designed an analogue switching circuit to control dis/charging of two supercapacitors to smooth power output.}
        \item {Wrote a report analysing the feasibility of converting homes into DC minigrids, optimsed for off-grid renewable energy.}
      \end{cvitems}
    }

  \cventry
    {} % Empty position
    {Product Expiry Tracker} % Project
    {Christchurch, New Zealand}
    {} % Empty date
    {
      \begin{cvitems}
        \item {Rapidly iterated using \textbf{Google App sheets} to integrate with existing systems and provide a user-friendly interface.}
        \item {Integrated with \textbf{Lightspeed PoS} Software over their \textbf{RESTful API} using \textbf{Python} to automate data entry.}
      \end{cvitems}
    }
\end{cventries}

%   \cventry
%     {} % Empty position
%     {Zero Robotics} % Project
%     {} % Empty location
%     {} % Empty date
%     {
%       \begin{cvitems} % Description(s) bullet points
%       	\item {Semifinalist out of 200 teams in MIT's international high school programming competition in C.}
% 		\item {Implemented 3D vector physics and game strategy for an autonomous satellite simulation using the ZR API.}
%       \end{cvitems}
%     }
